Title on one or two lines without capitals, except after a colon

### 2020-06-16 Report/main.tex
update section names
Update Report

\documentclass[10pt]{article}
\input{header}
\input{defs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Inferring Fine-Scale Animal Behaviors using Hidden Markov Models}
\author{Evan Sidrow}
\date{\today}

\begin{document}

\maketitle

\abstract

@@

%\input Sections/intro.tex
\input Sections/HHMM.tex
\input Sections/carHMM.tex
\input Sections/fourier.tex
\input Sections/simulation.tex
\input Sections/results.tex
\input Sections/conclusion.tex

>>>>

% Initial and revised submissions should be 12 point; this will be removed in the final version.
\documentclass[12pt]{TD-CJS}

% Initial and revised submissions should also be double spaced.  This command will be removed in the final version.
\renewcommand{\baselinestretch}{2}

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{psfrag}
\usepackage{graphicx}

\input{header}
\input{defs}

\begin{document}
\firstpage{1}
\lastpage{25}
\jvol{xx}
\issue{yy}
\jyear{2020}
\jid{CJS}
\aid{???}
% The running head contains the author names
\rhauthor{BlindedA and BlindedB}
\copyrightline{Statistical Society of Canada}
\Frenchcopyrightline{Soci\'et\'e statistique du Canada}
% History: received and accepted dates
\received{\rec{9}{July}{2009}}
\accepted{\acc{8}{July}{2010}}

% User-defined commands go here
\renewcommand{\eqref}[1]{(\ref{#1})}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mt}[1]{\mathrm{#1}}
\newcommand{\rv}{random variable}

% Title, authors, affiliations
\title[]{Title on one or two lines without capitals, except after a colon}%\query{Q1}
\author{BlindedA\authorref{1}\thanksref{*}}
\author{BlindedB\authorref{2}}
\affiliation[1]{Author affiliations will go here in the accepted manuscript, 
but do NOT include them in your initial submission because it must be anonymous.}
\affiliation[2]{Second Affiliation}

% Abstract, keywords, and classification codes
\startabstract{%
\keywords{
\KWDtitle{Key words and phrases}
Association parameters\sep clustered data\sep mean parameters\sep missing data\sep pairwise
likelihood\sep repeated measurements.
% MSC 2010 subject classification codes
\KWDtitle{MSC 2010}Primary 62???\sep secondary 62???}
\begin{abstract}
\abstractsection{}
\abstractsection{Abstract}
Insert your abstract here; it should
typically be up to ten lines long. Avoid symbols as much as possible. Formulas
are strongly discouraged, and citations should be avoided. 
The title and the abstract should be concise and descriptive;
list the key words in alphabetical order.  The MSC 2010 subject classification codes can be found here:
http://www.ams.org/mathscinet/msc/pdfs/classifications2010.pdf.

@@

\abscopyright
\fabstractsection{}
\fabstractsection{R\'{e}sum\'{e}}
Ins\'{e}rer votre r\'{e}sum\'{e}
ici. We will supply a French abstract for those authors who
can't prepare it themselves.\Frenchabscopyright
\end{abstract}}
\makechaptertitle

% Email address for corresponding author
\correspondingauthor[*]{\\\email{Insert your email address here only after your paper has been accepted}}

%\input Sections/intro.tex
\input Sections/background.tex
\input Sections/carhmm_ou.tex
\input Sections/model.tex
\input Sections/simulation.tex
\input Sections/results.tex
\input Sections/conclusion.tex
